Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-10-07 ms.tex
showing oscillatory behavior with the subarray. I wonder what's causing it.

\begin{figure*}
\gridline{
\fig{ap_labels_azlab06sub320Baseline487_NRCSUB320LED6P0MA.pdf}{0.3\textwidth}{Detector 487}\\
\fig{ap_labels_azlab06sub320Baseline488_NRCSUB320LED6P0MA.pdf}{0.3\textwidth}{Detector 488}
}
\gridline{
\fig{ap_labels_azlab06sub320Baseline489_NRCSUB320LED6P0MA.pdf}{0.3\textwidth}{Detector 489}\\
\fig{ap_labels_azlab06sub320Baseline490_NRCSUB320LED6P0MA.pdf}{0.3\textwidth}{Detector 490}
}
\caption{Source apertures (labeled ``0'') and horizontally-displaced background apertures for the AZLab 06 $320 \times 320$ subarray test.}\label{fig:sub320AperturesAZlab06}
\end{figure*}

\begin{figure*}
\gridline{
\fig{individual_azlab06_baseline3.pdf}{0.49\textwidth}{Stripe Baseline $2048 \times 256$}\\
\fig{individual_azlab06_sub320_6p0mA}{0.49\textwidth}{Subarray Baseline $320 \times 320$}
}
\caption{The time series of the AZLab 06 $320 \times 320$ subarray shows considerably higher scatter than the stripe mode.}\label{fig:sub320vsStripeBaseline2}
\end{figure*}

>>>>

\begin{figure*}
\gridline{
\fig{ap_labels_azlab06sub320Baseline487_NRCSUB320LED6P0MA.pdf}{0.3\textwidth}{Detector 487}\\
\fig{ap_labels_azlab06sub320Baseline488_NRCSUB320LED6P0MA.pdf}{0.3\textwidth}{Detector 488}
}
\gridline{
\fig{ap_labels_azlab06sub320Baseline489_NRCSUB320LED6P0MA.pdf}{0.3\textwidth}{Detector 489}\\
\fig{ap_labels_azlab06sub320Baseline490_NRCSUB320LED6P0MA.pdf}{0.3\textwidth}{Detector 490}
}
\caption{Source apertures (labeled ``0'') and horizontally-displaced background apertures for the AZLab 06 test with a $320 \times 320$ subarray test.}\label{fig:sub320AperturesAZlab06}
\end{figure*}

\begin{figure*}
\gridline{
\fig{individual_azlab06_baseline3.pdf}{0.49\textwidth}{Stripe Baseline $2048 \times 256$}\\
\fig{individual_azlab06_sub320_6p0mA}{0.49\textwidth}{Subarray Baseline $320 \times 320$}
}
\gridline{
\fig{individual_azlab06_sub320_6p0mA_t100_110.pdf}{0.49\textwidth}{5-15 min Zoom $320 \times 320$}\\
\fig{individual_azlab06_sub320_6p0mA_t005_t015.pdf}{0.49\textwidth}{100-110 min Zoom $320 \times 320$}
}
\caption{The time series of the AZLab 06 $320 \times 320$ subarray shows considerably higher scatter than the stripe mode.
A zoom-in on the $320 \times 320$ subarray time series shows that it exhibits oscillations every 4 integrations.
}\label{fig:sub320vsStripeBaseline2}
\end{figure*}
